\documentclass[11pt]{article}

\usepackage{xfp}
\usepackage[margin=0.5in]{geometry}
\usepackage{textcomp}
\usepackage{pgfplots}
\pgfplotsset{width=14cm,compat=1.9}

\title{Progress}
\author{Aheer Srabon}
\date{}

\begin{document}
\maketitle

\section*{June 2025}

\input{~/dotfiles/progress/months/june}

\subsection*{Targets}
\noindent There are no issues, there is nobody to fight to. I need to have the mentality to,

\begin{enumerate}
\itemsep0em
  \item Analyze
  \item Accept
  \item Orchestrate
\end{enumerate}

\noindent Being hard on myself has never worked out. I need,

\begin{itemize}
\itemsep0em
  \item A good GRE score.
  \item Freelancing with Python and Statistics.
  \item Fit body.
\end{itemize}

\noindent Depending on the situation, I'll be making adjustments. But I must realize the position I am currently
on and my drive to snap out of it.

\noindent If I deem that my preparation is good enough for GRE, I am going to spend less time on GRE.

\subsection*{Completed so far}
\begin{itemize}
\itemsep0em
  \item GRE           - \juneGRE hours
  \item CP \& DSA     - \juneDSACP hours
  \item Data Science  - \juneDS hours
  \item Python        - \junePYTHON hours
  \item Research      - \juneRESEARCH hours
  \item Investing     - \juneINVEST hours
\end{itemize}

\noindent Total: \juneTOTAL{} hours. Per day: \fpeval{\juneTOTAL / 30}.

\vspace{0.5cm}

\begin{tikzpicture}
    \begin{axis}[
        symbolic x coords={GRE, CP and DSA, Python, Data Science, Investing, Research},
        xtick=data
      ]
        \addplot[ybar] coordinates {
            (GRE,           \juneGRE)
            (CP and DSA,    \juneDSACP)
            (Data Science,  \juneDS)
            (Python,        \junePYTHON)
            (Research,      \juneRESEARCH)
            (Investing,     \juneINVEST)
        };
    \end{axis}
\end{tikzpicture}

\section*{July 2025}
\input{~/dotfiles/progress/months/july}

\noindent Last month, I did ok. While ok is ok, it is unfortunately not good enough. I decided to take
my GRE exam on August 2nd. So I have 31 days this month. I must work for 6 hours a day.

\subsection*{Targets}
\noindent This month, I am going to focus on only four things,
\begin{itemize}
  \item GRE
  \item Data Science and Research
  \item Investing
  \item Fitness
\end{itemize}

\noindent I am going to obliterate these four. On average, I wish to study 6 hours a day, at least 3 to 4 of
which should be allocated for GRE. I MUST get 340 on the GRE. It is hard, and that is precisely why I need it.
Also, I wish to lower my body weight by at least 3 kg in this month.

\subsection*{Completed so far}
\begin{itemize}
\itemsep0em
  \item GRE                       - \julyGRE hours
  \item Data Science \& Research  - \julyDSandRESEARCH hours
  \item Investing                 - \julyINVEST hours
\end{itemize}

\noindent Total: \julyTOTAL{} hours. Per day: \fpeval{\julyTOTAL / 1}.

\vspace{0.5cm}

\begin{tikzpicture}
    \begin{axis}[
        symbolic x coords={GRE, Data Science \& Research, Investing},
        xtick=data
      ]
        \addplot[ybar] coordinates {
            (GRE,                       \julyGRE)
            (Data Science \& Research,  \julyDSandRESEARCH)
            (Investing,                 \julyINVEST)
        };
    \end{axis}
\end{tikzpicture}

\end{document}
